Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-08 paper/manuscript.tex
some progress on Intro

\documentclass[11pt]{article}
\usepackage[round,semicolon]{natbib}
\usepackage[margin=1.3in]{geometry}
\usepackage{kpfonts}

@@

\section*{INTRODUCTION}
Nearly all viruses exhibit some antigenic variation.
However, the extent of this variation ranges widely across viruses and antibodies.
Broadly neutralizing antibodies against influenza virus are of great interest... \cite{corti2017tackling}.

>>>>

\documentclass[11pt]{article}
\usepackage[round,semicolon]{natbib}
\usepackage[margin=1.4in]{geometry}
\usepackage{kpfonts}

@@

\section*{INTRODUCTION}
Nearly all viruses show some antigenic variation.
However, the extent of this variation ranges widely.
For instance, although both measles virus~\citep{birrer1981antigenic,ter1981antigenic} and polio virus~\citep{crainic1983natural,diamond1985antigenic,drexler2014robustness} exhibit antigenic variation, the magnitude of this variation is small. 
Therefore, immunity elicited by infection or vaccination provides life-long protection against both these viruses~\citep{?}.
In contrast, some other viruses exhibit much more extensive antigenic variation.
An example is human influenza virus.
Infection with influenza virus provides life-long immunity to the infecting strain~\citep{?}.
But influenza virus undergoes such rapid antigenic evolution that the effectiveness of this immunity to antigenically drifted viral strains is almost completely eroded within a few years~\citep{?}.

Many explanations have been suggested for the differences in extent of antigenic variation among viruses, including epidemiological factors, the breadth of the immune response, and the virus's inherent evolutionary capacity to escape immunodominant antibody specificities~\citep{lipsitch2007patterns,cobey2014pathogen,fulton2015mutational}.
Here we will focus on the last of these explanations, as it provides the underlying rationale for recent efforts to develop a ``universal'' influenza vaccine that protects against a wide range of viral strains.

According to this inherent evolutionary capacity explanation, human influenza virus undergoes rapid antigenic drift because most neutralizing antibodies target epitopes on the viral hemagglutinin protein that are highly tolerant of mutational change.
This explanation is supported by classic experiments showing that it is easy to select viral mutants that completely escape most anti-hemagglutinin antibodies~\citep{}, as well as by the observation that single mutations that cause large changes in antigenicity arise frequently during the natural evolution of human influenza virus at the global scale~\cite{?} and even within individual humans with long-term infections~\cite{?}.
A corollary of this explanation is that the virus's capacity for antigenic drift would be greatly reduced if most antibodies instead targeted epitopes

This corollary has become of more than academic interest with the discovery of broadly neutralizing antibodies.

Of course, it remains unclear if these epitopes are more conserved because they are inherent intolerant or just aren't under pressure.
For instance, non-human influenza doesn't undergo much antigenic drift.
Knowing is important because success of a vaccine would put them under pressure.

Broadly neutralizing antibodies against influenza virus are of great interest... \cite{corti2017tackling}.
